Items

### 2021-08-26 items.rmd
- updated for website

---
title: "Items"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
      toc_depth: 3
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
# pdf_document:
#   toc: TRUE
---

>>>>

---
title: "Items"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
      toc_depth: 3
---
